Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-03-07 ch02-qlogms/excitation-design.tex
Address some TODOs

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics~\citep{Steinbuch1998,Oomen2016}, vibration analysis~\citep{Karnopp1995,Voorhoeve2015SYSID} and acoustics testing amongst others. %TODO reference acoustics (ISMA?)

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment coefficient $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (see \eqref{eq:excitation:optimAlpha}).}
    \label{fig:excitation:worstCaseBeta}
  \end{figure}

@@

  \begin{figure}[ht]
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.
             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
    \label{fig:excitation:worstCaseAlpha}
  \end{figure}

@@

@@

    \begin{figure}%
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
    \TODO{use styles from above}
      \label{fig:excitation:measurements}
    \end{figure}

@@

\TODO{move this guideline somewhere else}
\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of many sharp resonance peaks over a wide frequency band of interest with a constant quality.
\end{guideline}

>>>>

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics~\citep{Steinbuch1998,Oomen2016}, vibration analysis~\citep{Karnopp1995,Voorhoeve2015SYSID} and acoustic testing~\citep{GarciaLopez2014,DAmico2014} amongst others.

@@

  \begin{figure}[pht]
    \centering
    \remakeNextFigure
      \setlength\figurewidth{0.63\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment coefficient $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (see \eqref{eq:excitation:optimAlpha}).}
    \label{fig:excitation:worstCaseBeta}
  \end{figure}

@@

  \begin{figure}[pht]
    \centering
    \remakeNextFigure
      \setlength\figurewidth{0.63\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.
             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
    \label{fig:excitation:worstCaseAlpha}
  \end{figure}

@@

\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of multiple sharp resonance peaks over a wide frequency band of interest with a constant quality.
\end{guideline}

@@

    \begin{figure}%
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}
      \label{fig:excitation:measurements}
    \end{figure}

@@

### 2016-03-07 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Address some TODOs

\TODO{paper $\to$ section}

\TODO{use gls commands in this part}

@@

\paragraph{Formulation of the Linear LS LPM}
The \gls{LPM} is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
\citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems.
The formulation in this section is a summary for a \gls{SISO} system.

>>>>

@@

\paragraph{Formulation of the Linear LS LPM}
The \gls{LPM} is formulated as a nonparametric local linear \gls{LS} estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}.
\citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems.
The formulation in this section is a summary for a \gls{SISO} system.

### 2016-03-07 ch04-lrmhinf/conference.tex
Address some TODOs

% arara: pdflatex: { shell : yes }
% arara: bibtex
% arara: makeglossaries
% arara: pdflatex: { shell : yes, synctex : yes}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{xspace}
smart
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{tangocolors}
\usepackage{tikz}
\usetikzlibrary{spy}
\usepackage{pgfplots}

\usepackage{color}
\newcommand{\EDIT}{\textcolor{red}{EDIT}}

\newlength\figureheight 
\newlength\figurewidth

%\usepackage{hyperref}

@@

\usepackage{graphicx}
\graphicspath{{./figures/}{.}{./tikz/}}

\newcommand{\TODO}[1]{ {\color{red} #1} }

@@

\begin{document}

\begin{frontmatter}

\title{Enhancing \Hinf{} Norm Estimation using Local LPM/LRM  Modeling: Applied to an AVIS\thanksref{thx}}

\thanks[thx]{This work is supported by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem), and by the Belgian Government through the Interuniversity Poles of Attraction (IAP VII-Dysco) Program, the Innovational Research Incentives Scheme under the VENI grant ``Precision Motion: Beyond the Nanometer'' (no. 13073) awarded by NWO (Netherlands Organization for Scientific Research) and STW (Dutch Science Foundation).}

\author[VUB]{Egon Geerardyn} 
\author[TUE]{Tom Oomen} 
\author[VUB]{Johan Schoukens}

\address[VUB]{ELEC Department, Vrije Universiteit Brussel, Brussels, Belgium. \\ (e-mails: \href{mailto:egon.geerardyn@vub.ac.be}{egon.geerardyn}, \href{mailto:johan.schoukens@vub.ac.be}{johan.schoukens} @vub.ac.be)}
\address[TUE]{Control System Technology Group, Mechanical Engineering Department, Technische Universiteit Eindhoven, Eindhoven, the Netherlands. (e-mail: \href{mailto:t.a.e.oomen@tue.nl}{t.a.e.oomen@tue.nl})}

\begin{keyword}
Frequency-response;
Uncertainty;
Norms;
Estimation;
Polynomials;
Signal Processing;
System Identification;
Robust Control.
\end{keyword}

\begin{abstract}~
Accurate uncertainty modeling is of key importance in high performance robust control design. 
The aim of this paper is to develop a new uncertainty modeling procedure that leads to enhanced accuracy for the $\mathcal{H}_\infty$ norm. 
A frequency response based approach is adopted. 
The key novelty of this paper is a new method to address the intergrid error using local parametric modeling methods. 
These local polynomial and rational models enhance the estimates at the discrete frequency grid.
Moreover, the presented methods are shown to enhance the intergrid error estimate.
This is illustrated using simulations and experiments on an industrial active vibration isolation system.
Compared to the local polynomial models, local rational models are able to handle lightly-damped resonances using far fewer data points, which means that measurement time can be kept short.
\end{abstract}

\end{frontmatter}

@@

%TODO: acknowledgments reviewers

\bibliography{biblio/references,biblio/ownWork} 
%\bibliographystyle{ifacconf}

>>>>

@@

@@

% \begin{document}

% \begin{frontmatter}

% \title{Enhancing \Hinf{} Norm Estimation using Local LPM/LRM  Modeling: Applied to an AVIS\thanksref{thx}}

% \thanks[thx]{This work is supported by the Fund for Scientific Research (FWO-Vlaanderen), by the Flemish Government (Methusalem), and by the Belgian Government through the Interuniversity Poles of Attraction (IAP VII-Dysco) Program, the Innovational Research Incentives Scheme under the VENI grant ``Precision Motion: Beyond the Nanometer'' (no. 13073) awarded by NWO (Netherlands Organization for Scientific Research) and STW (Dutch Science Foundation).}

% \author[VUB]{Egon Geerardyn} 
% \author[TUE]{Tom Oomen} 
% \author[VUB]{Johan Schoukens}

% \address[VUB]{ELEC Department, Vrije Universiteit Brussel, Brussels, Belgium. \\ (e-mails: \href{mailto:egon.geerardyn@vub.ac.be}{egon.geerardyn}, \href{mailto:johan.schoukens@vub.ac.be}{johan.schoukens} @vub.ac.be)}
% \address[TUE]{Control System Technology Group, Mechanical Engineering Department, Technische Universiteit Eindhoven, Eindhoven, the Netherlands. (e-mail: \href{mailto:t.a.e.oomen@tue.nl}{t.a.e.oomen@tue.nl})}

% \begin{keyword}
% Frequency-response;
% Uncertainty;
% Norms;
% Estimation;
% Polynomials;
% Signal Processing;
% System Identification;
% Robust Control.
% \end{keyword}

% \begin{abstract}~
% Accurate uncertainty modeling is of key importance in high performance robust control design. 
% The aim of this paper is to develop a new uncertainty modeling procedure that leads to enhanced accuracy for the $\mathcal{H}_\infty$ norm. 
% A frequency response based approach is adopted. 
% The key novelty of this paper is a new method to address the intergrid error using local parametric modeling methods. 
% These local polynomial and rational models enhance the estimates at the discrete frequency grid.
% Moreover, the presented methods are shown to enhance the intergrid error estimate.
% This is illustrated using simulations and experiments on an industrial active vibration isolation system.
% Compared to the local polynomial models, local rational models are able to handle lightly-damped resonances using far fewer data points, which means that measurement time can be kept short.
% \end{abstract}

% \end{frontmatter}

@@
